Canonical rings of $\bq$-divisors on Minimal Rational Surfaces

### 2015-07-30 surfaces-write-up/surface-write-up.tex
responses to peter's comments such as trying to standardize the use of the term extremal rays

\begin{rem}\todo{Peter: maybe move this out of a remark and just say it with the previous example?  As it stands, the previous example is a little unclear as to what its purpose is...}
\label{rem:ghost-motivation}
Example ~\ref{eg:hyperplane} shows that the naive generalization of
~\cite[Theorem 8]{dorney:canonical} of generation in degree at most
$\sum_{i=1}^{n}\ell_i$ cannot possibly hold. The reason for this is
that the divisors may ``be contained in a hyperplane,'' i.e.~ be
expressible as functions in $m$ of the $m+1$ variables on $\bp^m$.
This problem can easily be circumvented by adding in ``ghost
points.'' That is, we may add divisors of the form $0 \cdot H_i$ to
$D$, and reorder so that if $D = \sum_{i=1}^{n}\alpha_i V(f_i)$,
then $\bk[f_0, \ldots, f_m]$ has transcendence degree $m+1$ over $\bk$.

@@

\end{lem}
\begin{proof}
Let 
\begin{align}\label{eqn:Sigma-def}
	\Sigma = \left \{(d, c_1, \ldots, c_n) \in \bz^{n+1} : c_i \geq - d
\alpha_i, \; 1 \leq i \leq n, \text{ and } \sum_{i=1}^{n} \ell_i \bida_i = 0
\right \}.
\end{align}
\todo{Aaron: Possibly take this definition out of the proof, and move it into the setup, since we want to reference it later.  \\
Peter: I like having the statement of the lemma being nice and consise; also the statement has nothing to do with this geometric picture, so I find it more natural to have the geometric side contained in the proof.  I also don't quite see why it is so bad to reference something from inside a previous proof; a reader can surely locate it...
}
We note that $\Sigma$ has extremal rays given by the lattice points 
\begin{equation}\label{defn:e-i-proj}
	e_i = \left(\ell_i \bida_i, - \alpha_1 \ell_i \bida_i, \ldots
-\alpha_{i-1} \ell_i \bida_i, \ell_i \sum_{j\ne i} \alpha_j \bida_j,
-\alpha_{i+1} \ell_i \bida_i, \ldots, -\alpha_n, \ell_i \bida_i \right)
\end{equation}
for each $i\in \{1, \ldots n\}$.
Therefore, applying Proposition ~\ref{prop:cone-generation}, we see $R_D$ is generated in degrees less than
\[
	\sum_{i=1}^n \ell_i a_i.
\]
\end{proof}

@@

For the remainder of this section we will assume $D_1, D_2, D_3,$ and $D_4$ are
distinct divisors with bi-degrees $(1,0)$
, $(1,0)$, $(0,1)$, and $(0,1)$ respectively. Let $D_i = V(f_i)$ where
$f_i \in \sco(\bida_i, \bidb_i)$.  
Then, $f_1$ and $f_2$ are independent linear
polynomials in $x_0$ and $x_1$ and $f_3$ and $f_4$ are independent
linear polynomials in $y_0$ and $y_1$.  In order to achieve this condition on $D_1, \ldots D_4$, it may be necessary to add in ``Ghost Divisors'' (i.e. divisors with of the desired form with a coefficient $\alpha_i = 0$).
\begin{defn}
Define 
\begin{equation}
\label{eqn:define-T=(D)}
	\Te(D) = \left\{i \in \{1, \ldots, n\}: \bida_i \sum_{k=1}^n \bidb_k 
\alpha_k = \bidb_i \sum_{k=1}^n \bida_k \alpha_k \right\},
\end{equation}

@@

The extremal rays of $\Sigma \otimes_\bz \bq$ can be represented by points
lying only on the edges 
$\overline{e_i e_j}$.
The extremal rays are spanned by those $e_i$'s
which are contained in $H$ together with intersection points $e_{i, j}$ which
can be expressed as $H \cap \overline{e_i e_j},$ where $i \neq j$ and $e_i,
e_j \notin H$. Note that $e_{i,j}$ is only defined in the case
$\# \{H \cap \overline{e_i, e_j}\} = 1$.

From this we can deduce the representatives of $\Sigma$ lying on its extremal rays given by the following:
For $i \in \Te(D)$, define $e_i \in R_D$ in degree $d_i = \ell_i \gcd(a_i, b_i)$ by 
\begin{equation}\label{eqn:epsilon_i}
	e_i := (-\alpha_1 d_i, \ldots, - \alpha_{i-1} d_i, \frac{d_i}{\bida_i + \bidb_i}\sum_{k \ne i}
	\alpha_k (\bida_k + \bidb_k), - \alpha_{i+1} d_i, \ldots, - \alpha_n d_i)
\end{equation}

\noindent
For $i \in \Tp(D)$ and $j \in \Tm(D)$, define $e_{i,j}\in R_D$ in degree $d_{i,j} = \ell_{i, j}(\bida_i \bidb_j - \bida_j \bidb_i)$ by
\begin{equation}\label{eqn:epsilon_i,j}
	\begin{split}& e_{i,j} := (-\alpha_1 d_{i,j}, \ldots -\alpha_{i-1} d_{i,j}, \bidb_j \sum_{k \ne i,j} \alpha_k \bida_k - \bida_j \sum_{k \ne i, j}
	\alpha_k \bidb_k, -\alpha_{i+1} d_{i,j}, \\
	&\ldots -\alpha_{j-1} d_{i,j}, -\bidb_i \sum_{k \ne i, j} \alpha_k \bida_k + \bida_i \sum_{k \ne i, j}
	\alpha_k \bidb_k, -\alpha_{j+1}d_{i,j}, \ldots, - \alpha_{n}d_{i,j}).
	\end{split}
\end{equation}
Note that the above expression is for when $i < j$, but a small rearangement gives when $j < i$.  \todo{Peter: I changed the above expression, but I'm still feel a little dubious that this is easier to read...}

@@

A quick calculation deduces that these $e_i$'s and
$e_i{i,j}$'s lie on the extremal rays of $\Sigma$.
%\begin{rem}
%For the remainder of this section replace the $e_i$'s and $e_{i,j}$'s with a %(possibly) different representative of it's extremal ray say that their lattice points %correspond to the $\epsilon_i$'s and $\epsilon_{i,j}$'s, respectively.
%\end{rem}

@@

To find such a $\beta_i$,
we simply write $f_i$ as a 
polynomial in $f_1, \ldots f_4$. Furthermore, these
generate all relations, since they allow us to reduce any $\prod_{j =
1}^n f_j^{c_j}$ to the canonical form where $r_i = - \lfloor d \alpha_i
\rfloor$ whenever $i > 4$.

%Note that we can view a relation from Equation
%~\ref{eqn:hirz-relations-psi} as an element of $S$ given
%by $(d, c_1, \ldots, c_{i-1}, c_i + 1, c_{i+1}, \ldots , c_n)$.  
Let $\Omega\subseteq \Sigma$ be the 
set
\begin{align*}
	\Omega = & \{(d, c_1, \ldots, c_{i-1}, c_i + 1, c_{i+1}, \ldots , c_n)  \in \bz^{n+1}_{\geq 0} : \\
	& c_i \ge -\alpha_i d, \text{ for all i, and } \bida_i + \sum_{j = 1}^m \bida_j c_j = \bidb_i + \sum_{j=1}^n \bidb_j c_j
= 0 \}
\end{align*}

Let $\omega\in \Omega'$ correspond to the monomial $y_i \prod_{j=1}^n
{y_j}^{c_j}$.  Then we can write $\omega$ as a sum of $r_j e_j$'s for $j\in
\Te$ and $r_{j,k}e_{j,k}$ for $j\in \Tp, k\in \Tm$.  
For convenience, let $e_j$ (when it exists) be in degree $d_j$ with $j^{th}$
component $-\alpha_j d_j + \kappa_j$ for some $\kappa_j \in \bq$ and let $e_{j,k}$ (when it exists) lie in
degrees $d_{j,k}$ with $j^{th}$ component $-\alpha_j d_{j,k} + \kappa_{j,k}'$ and $k^{th}$
component $-\alpha_j d_{j,k} + \kappa_{j,k}''$ for $\kappa_{j,k}', \kappa_{j,k}'' \in \bq$
By a careful computation, we can find $\lambda \in \Sigma$ 
\todo{Aaron: Is it at all possible to write down what $\lambda$ and the $r_{i,j}$ are?
I suspect we should be able to write them in a couple lines, which would
definitely clarify how we're getting the bound on degree $E$. While I agree
it's fine to hide the computation of the $r_{i,j}$ it would still clarify matters
to say what the $r_{i,j}$ and $\lambda$ are.
\\
Peter: There is not a unique choice of the $r_{i,j}$'s.  When we write out $\sigma$ in terms of the $e_i$'s and $e_{i,j}'s$ with coefficients $C_i$ and $C_{i,j}$, any choice of $r_{i,j}$'s that are at most equal to the coefficient $C_{i,j}$ and such that $\sum_{j\in T_-} r_{i,j}\kappa'_{i,j}=1$ will work.}
and $r_{i,j} \in \bq$ (in general such a choice may be very non-unique) so that we can write
\begin{equation}\label{eqn:sigma-in-terms-of-lambda/E}
	\sigma = \lambda + E
 \end{equation}
with $E$ of the form
\begin{equation}\label{eqn:hirz-E-translation}
	E = \begin{cases}
	\frac{1}{\kappa_i} e_i  	&  \mbox{ if }i\in \Te\\
	\sum_{j\in \Tm} r_{i,j} e_{i,j}: r_{i,j}\in \bq, \sum_{j\in \Tm} r_{i,j}\kappa_{i,j}' = 1 & \mbox{ if } i\in \Tp\\
	\sum_{j\in \Tp} r_{j,i} e_{j,i}: r_{j,i} \in \bq, \sum_{j\in \Tm} r_{j,i} \kappa_{i,j}'' = 1 	& \mbox{ if } i\in \Tm\\
	\end{cases}.
\end{equation}

@@

However, I'm really baffled as to why you want to apply $\psi$ to the
$\beta_i$, since two lines later, you then apply the reverse correspondence
and want to work back in the semigroupring. Why don't you just stay in the
semigroup ring the whole time?
I think I'm misunderstanding this, but is $\omega_\mu$ just equal to
$\beta_i$ for some $i$? Also, why is $\omega_\mu$ missing a $d$ index
as its first index?
\\
Peter: $\beta_i$'s are polynomials in $f_1, \ldots f_4$.  By the monomial terms in $\beta_i$ I mean look at each monomial appearing in this polynomial and take the set of those.
}
can further compute that there exist $q_i, q_{i,j} \in \bq_{\geq 0}$ and $\lambda \in
\Sigma$ so that the lattice point, $\omega_\mu = (c_1 ,\ldots c_n)$,
corresponding to $\mu
$ is of the form
\[
	\omega_\mu = \lambda + E_\mu
\]
where $\lambda$ is the same as in Equation \ref{eqn:sigma-in-terms-of-lambda/E} and $E_\mu$ is defined in a similar fashion as $E$ in Equation \ref{eqn:hirz-E-translation} by
\begin{equation}\label{eqn:hirz-E_mu-translation}
E_\mu = \left(\sum_{\substack{i \in \{1, 2, 3, 4\} \cap \Te}}q_i e_i\right) +
\left(\sum_{\substack{i \in \{1, 2, 3, 4\} \cap \Tp \\ j\in \Tm}} q_{i,j}
e_{i,j}\right) + \left(\sum_{\substack{i \in \{1, 2, 3, 4\} \cap \Tm \\ j\in
\Tp}} q_{j,i} e_{i,j}\right).
\end{equation}
\todo{Aaron: if $\sigma_\mu$ is an element, how can it be written as
	the sum of an element and a set? Same question for $\sigma$ above.
	Also, I do not know what $E_\mu$ is. You really have to define it,
since there's no way to check the validity of this proof without it.  \\
Peter: $E$ and $E_\mu$ are elements, not sets...

Aaron: My mistake. Thanks for writing it out though. However,
since $E, E_\mu$ are so similar, why not defining them so that they look similar?
I.e., why not define them either both in three cases as $E$
or both as sums as $E_\mu$. It's confusing that they are the same, but not
written in a parallel fashion.
\\
Peter: Well... We had a conversation a while ago that saying something like $j \in \{i\} \cap T_=$ might look a little funny (saying $j$ ranging over the set of i intersect $T_=$ meaning $j$ either ranges over the emptyset or the singleton set of $i$).  I We could make this change in the first one if it is preferable.  On the other hand, transforming the second into the form of the first would be terribly ugly (like 12 cases, some of which are sumed together... or something like that...).
}
Note that $E_\mu$ lies in the same degree as $E$ for all $\mu$.

Let $F\in R_D$ corresponding to the lattice point $E$ and let $F_\mu$ correspond to the lattice point $E_\mu$.  
Then $F - \sum_{\mu \in M} F_\mu = 0$ induces a
relation in degree at most
\[
	\rho + \deg(F)
\]

>>>>

\begin{rem}\todo{Peter: maybe move this out of a remark and just say it with the previous example?  As it stands, the previous example is a little unclear as to what its purpose is...}
\label{rem:ghost-motivation}
Example ~\ref{eg:hyperplane} shows that the naive generalization of
~\cite[Theorem 8]{dorney:canonical} of generation in degree at most
$\sum_{i=1}^{n}\ell_i$ cannot possibly hold. The reason for this is
that the divisors may ``be contained in a hyperplane,'' i.e.~ be
expressible as functions in $m$ of the $m+1$ variables on $\bp^m$.
This problem can easily be circumvented by adding in ``ghost
points.'' That is, we may add divisors of the form $0 \cdot H_i$ to
$D$, and reorder so that if $D = \sum_{i=1}^{n}\alpha_i V(f_i)$,
then $f_0, \ldots, f_m$ cut out linearly independent
hyperplanes in $\bp^m$.

@@

\end{lem}
\begin{proof}
Let 
\begin{align}\label{eqn:Sigma-def}
	\Sigma = \left \{(d, c_1, \ldots, c_n) \in \bz^{n+1} : c_i \geq - d
\alpha_i, \; 1 \leq i \leq n, \text{ and } \sum_{i=1}^{n} \ell_i \bida_i = 0
\right \}.
\end{align}
\todo{Aaron: Possibly take this definition out of the proof, and move it into
	the setup, since we want to reference it later.  \\
Peter: I like having the statement of the lemma being nice and consise; also
the statement has nothing to do with this geometric picture, so I find it more
natural to have the geometric side contained in the proof.  I also don't quite
see why it is so bad to reference something from inside a previous proof; a
reader can surely locate it...

Aaron: In general, I like the idea of having proofs self contained,
so that one should only refer to the proof statement, not the
body of the proof.
I'm not very strongly tied to this idea though, and I think it's fine. I think it's fine.
}
We note that $\Sigma$ has extremal rays given by the lattice points 
\begin{equation}\label{defn:e-i-proj}
	e_i = \left(\ell_i \bida_i, - \alpha_1 \ell_i \bida_i, \ldots
-\alpha_{i-1} \ell_i \bida_i, \ell_i \sum_{j\ne i} \alpha_j \bida_j,
-\alpha_{i+1} \ell_i \bida_i, \ldots, -\alpha_n, \ell_i \bida_i \right)
\end{equation}
for each $i\in \{1, \ldots n\}$.
Therefore, applying Proposition ~\ref{prop:cone-generation}, we see $R_D$ is generated in degrees less than
\[
	\sum_{i=1}^n \ell_i a_i.
\]
\end{proof}

@@

For the remainder of this section we will assume $D_1, D_2, D_3,$ and $D_4$ are
distinct divisors with bi-degrees $(1,0)$
, $(1,0)$, $(0,1)$, and $(0,1)$ respectively. Let $D_i = V(f_i)$ where
$f_i \in \sco(\bida_i, \bidb_i)$.  
Then, $f_1$ and $f_2$ are independent linear
polynomials in $x_0$ and $x_1$ and $f_3$ and $f_4$ are independent
linear polynomials in $y_0$ and $y_1$.  In order to achieve this condition on
$D_1, \ldots D_4$, it may be necessary to add in ``Ghost Divisors'' (i.e.
divisors with of the desired form with a coefficient $0$).
\begin{defn}
Define 
\begin{equation}
\label{eqn:define-T=(D)}
	\Te(D) = \left\{i \in \{1, \ldots, n\}: \bida_i \sum_{k=1}^n \bidb_k 
\alpha_k = \bidb_i \sum_{k=1}^n \bida_k \alpha_k \right\},
\end{equation}

@@

The extremal rays of $\Sigma \otimes_\bz \bq$ can be represented by points
lying only on the edges 
$\overline{e_i e_j}$.
The extremal rays are given by multiples of those $\epsilon_i$'s
which are contained in $H$ together with intersection points $e_{i, j}$ which
can be expressed as $H \cap \overline{e_i e_j},$ where $i \neq j$ and $e_i,
e_j \notin H$. Note that $e_{i,j}$ is only defined in the case
$\# \{H \cap \overline{e_i, e_j}\} = 1$.

From this we can deduce that a set of extremal rays of $\Sigma$ are given as follows:
For $i \in \Te(D)$, define $e_i \in R_D$ in degree $d_i = \ell_i \gcd(a_i, b_i)$ by 
\begin{equation}\label{eqn:epsilon_i}
	e_i := (-\alpha_1 d_i, \ldots, - \alpha_{i-1} d_i, \frac{d_i}{\bida_i + \bidb_i}\sum_{k \ne i}
	\alpha_k (\bida_k + \bidb_k), - \alpha_{i+1} d_i, \ldots, - \alpha_n d_i)
\end{equation}

\noindent
For $i \in \Tp(D)$ and $j \in \Tm(D)$, with $i < j$, define $e_{i,j}\in R_D$ in degree $d_{i,j} = \ell_{i, j}(\bida_i \bidb_j - \bida_j \bidb_i)$ by
\begin{equation}\label{eqn:epsilon_i,j}
	\begin{split}& e_{i,j} := (-\alpha_1 d_{i,j}, \ldots -\alpha_{i-1} d_{i,j}, \bidb_j \sum_{k \ne i,j} \alpha_k \bida_k - \bida_j \sum_{k \ne i, j}
	\alpha_k \bidb_k, -\alpha_{i+1} d_{i,j}, \\
	&\ldots -\alpha_{j-1} d_{i,j}, -\bidb_i \sum_{k \ne i, j} \alpha_k \bida_k + \bida_i \sum_{k \ne i, j}
	\alpha_k \bidb_k, -\alpha_{j+1}d_{i,j}, \ldots, - \alpha_{n}d_{i,j}).
	\end{split}
\end{equation}
Note that the above expression makes sense when $i < j$, but one
can similarly define $e_{i,j}$ when $j < i$.  
\todo{Peter: I changed the above expression,
but I'm still feel a little dubious that this is easier to read...

Aaron: I agree this is harder to read. Why don't we just write
$e_{i,j} = a e_i + b e_j$ (where of course you replace a and b by explicit
constants). Wouldn't that be much cleaner? Also, I think we should
explicitly state what the small rearrangement is to switch 
$i$ and $j$, but perhaps it won't be relevant if you write $e_{ij} $
as a linear combination of $e_i, e_j$.}

@@

Since these $e_i$ are multiples of $\epsilon_i$ and these
$e_{i,j}$ are points of intersection of $H$ with
$\overline {e_ie_j}$ such that neither $e_i$ nor $e_j$
are contained in $H$, these form a set of extremal rays of $\Sigma$.
%\begin{rem}
%For the remainder of this section replace the $e_i$'s and $e_{i,j}$'s with a %(possibly) different representative of it's extremal ray say that their lattice points %correspond to the $\epsilon_i$'s and $\epsilon_{i,j}$'s, respectively.
%\end{rem}

@@

To find such a $\beta_i$,
\todo{Aaron: Shouldn't we say something above like, the kernel
	is bounded by the maximum of something over all $i$,
	so for the remainder of the proof, we fix an $i$.
	Also, I think it would help if things
	that depend on $i$, such as $E,\sigma,\lambda$
have an $i$ subscript.}
we simply write $f_i$ as a 
polynomial in $f_1, \ldots f_4$. Furthermore, these
generate all relations, since they allow us to reduce any $\prod_{j =
1}^n f_j^{c_j}$ to the canonical form where $r_i = - \lfloor d \alpha_i
\rfloor$ whenever $i > 4$.

%Note that we can view a relation from Equation
%~\ref{eqn:hirz-relations-psi} as an element of $S$ given
%by $(d, c_1, \ldots, c_{i-1}, c_i + 1, c_{i+1}, \ldots , c_n)$.  
Let $\Omega\subseteq \Sigma$ be the 
set
\begin{align*}
	\Omega = & \{(d, c_1, \ldots, c_{i-1}, c_i + 1, c_{i+1}, \ldots , c_n)  \in \bz^{n+1}_{\geq 0} : \\
	& c_i \ge -\alpha_i d, \text{ for all i, and } \bida_i + \sum_{j = 1}^m \bida_j c_j = \bidb_i + \sum_{j=1}^n \bidb_j c_j
= 0 \}.
\end{align*}

Let $\omega\in \Omega'$ correspond to the monomial $y_i \prod_{j=1}^n
{y_j}^{c_j}$.  Then we can write $\omega$ as a sum of $r_j e_j$'s for $j\in
\Te$ and $r_{j,k}e_{j,k}$ for $j\in \Tp, k\in \Tm$.  
For convenience, let $e_j$ (when it exists) be in degree $d_j$ with $j^{th}$
component $-\alpha_j d_j + \kappa_j$ for some $\kappa_j \in \bq$ and let $e_{j,k}$ (when it exists) lie in
degrees $d_{j,k}$ with $j^{th}$ component $-\alpha_j d_{j,k} + \kappa_{j,k}'$ and $k^{th}$
component $-\alpha_j d_{j,k} + \kappa_{j,k}''$ for $\kappa_{j,k}', \kappa_{j,k}'' \in \bq$
By a careful computation, we can find $\lambda \in \Sigma$ 
\todo{Aaron: Is it at all possible to write down what $\lambda$ and the $r_{i,j}$ are?
I suspect we should be able to write them in a couple lines, which would
definitely clarify how we're getting the bound on degree $E$. While I agree
it's fine to hide the computation of the $r_{i,j}$ it would still clarify matters
to say what the $r_{i,j}$ and $\lambda$ are.
\\
Peter: There is not a unique choice of the $r_{i,j}$'s.  When we write out $\sigma$ in terms of the $e_i$'s and $e_{i,j}'s$ with coefficients $C_i$ and $C_{i,j}$, any choice of $r_{i,j}$'s that are at most equal to the coefficient $C_{i,j}$ and such that $\sum_{j\in T_-} r_{i,j}\kappa'_{i,j}=1$ will work.

Aaron: OK. In that case, why don't you say that? Since I didn't understand those constraints on $r_{i,j}$, I think
the reader would probably also be lost without explicitly writing those constraints.
Also, what about $\lambda$? Is that uniquely determined?}
and $r_{i,j} \in \bq$ (in general such a choice may be very non-unique) so that we can write
\begin{equation}\label{eqn:sigma-in-terms-of-lambda/E}
	\sigma = \lambda + E
 \end{equation}
with $E$ of the form
\begin{equation}\label{eqn:hirz-E-translation}
	E = \begin{cases}
	\frac{1}{\kappa_i} e_i  	&  \mbox{ if }i\in \Te\\
	\sum_{j\in \Tm} r_{i,j} e_{i,j}: r_{i,j}\in \bq, \sum_{j\in \Tm} r_{i,j}\kappa_{i,j}' = 1 & \mbox{ if } i\in \Tp\\
	\sum_{j\in \Tp} r_{j,i} e_{j,i}: r_{j,i} \in \bq, \sum_{j\in \Tm} r_{j,i} \kappa_{i,j}'' = 1 	& \mbox{ if } i\in \Tm\\
	\end{cases}.
\end{equation}

@@

However, I'm really baffled as to why you want to apply $\psi$ to the
$\beta_i$, since two lines later, you then apply the reverse correspondence
and want to work back in the semigroupring. Why don't you just stay in the
semigroup ring the whole time?
I think I'm misunderstanding this, but is $\omega_\mu$ just equal to
$\beta_i$ for some $i$? Also, why is $\omega_\mu$ missing a $d$ index
as its first index?
\\
Peter: $\beta_i$'s are polynomials in $f_1, \ldots f_4$.  By the monomial terms in $\beta_i$ I mean look at each monomial appearing in this polynomial and take the set of those.
}
can further compute that there exist $q_i, q_{i,j} \in \bq_{\geq 0}$ 
\todo{Aaron: Would it be reasonable to given these $q_{ij}$ a $\mu$
superscript or subscript to indicate dependence on $\mu$?}
and $\lambda \in
\Sigma$ so that the lattice point, $\omega_\mu = (c_1 ,\ldots c_n)$,
corresponding to $\mu
$ is of the form
\[
	\omega_\mu = \lambda + E_\mu
\]
where $\lambda$ is the same as in Equation \ref{eqn:sigma-in-terms-of-lambda/E} and $E_\mu$ is defined by

\begin{equation}\label{eqn:hirz-E_mu-translation}
E_\mu = \left(\sum_{\substack{i \in \{1, 2, 3, 4\} \cap \Te}}q_i e_i\right) +
\left(\sum_{\substack{i \in \{1, 2, 3, 4\} \cap \Tp \\ j\in \Tm}} q_{i,j}
e_{i,j}\right) + \left(\sum_{\substack{i \in \{1, 2, 3, 4\} \cap \Tm \\ j\in
\Tp}} q_{j,i} e_{i,j}\right).
\end{equation}

Note that $E_\mu$ lies in the same degree as $E$ for all $\mu$.

Let $F\in R_D$ correspond to the lattice point $E$ and let $F_\mu$ correspond to the lattice point $E_\mu$.  
Then $F - \sum_{\mu \in M} F_\mu = 0$ induces a
relation in degree at most
\[
	\rho + \deg(F)
\]
